\documentclass[12pt]{article}

\usepackage{array}
\usepackage[top=1in, bottom=0.5in, left=0.75in, right=0.75in]{geometry}

\usepackage{titlesec}
\usepackage{titling}
\usepackage{tabu}
\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}


\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{}

\titlespacing{\section}{0em}{0em}{1em}
\titlespacing{\tabu}{0em}{0em}{-10em}

\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries Yue Niu}\\
\end{center}
}

\setlength\parindent{0pt}
\newcolumntype{?}{!{\vrule width 0.5pt}}

\begin{document}
\pagenumbering{gobble}
\maketitle

\section{Contact}
\begin{itemize}
\itemsep-2pt
\item Email: yuen@andrew.cmu.edu 
\item Web: github.com/kaonn 
\end{itemize}

\section{Research Interests}

Resource Analysis, Type Systems, Computational Complexity, Programming Language Semantics\\

\section{Education}

\begin{tabu} to \textwidth {@{}>{\bfseries} l  X[r] }
Ph.D. in Computer Science & Aug 2018 - Present
\end{tabu}

\vspace{-5pt}
\begin{itemize}
\itemsep-5pt
\item Carnegie Mellon University
\item Advisor: Robert Harper
\item Courses: 
   Quantitative Program Analysis,
   Parallel \& Concurrent Computation, 
   Algebraic Topology,
   Optimizing Compilers, 
   Artificial Intelligence
\end{itemize}

\begin{tabu} to \textwidth {@{}>{\bfseries} l X[r] }
B.S. in Computer Science, Minor in Physics & Aug 2014 - Dec 2017
\end{tabu}

\vspace{-5pt}
\begin{itemize}
\itemsep-2pt
\item Carnegie Mellon University
\item Research Advisor: Jan Hoffmann
\item GPA: 3.76
\item Honors: Dean's List for School of Computer Science (Fall 2014, Fall  2015, Spring 2017)
\item Courses: 
   Compiler Design,
   Programming Languages, 
   Constructive Logic, Formal Logic, 
   Computability Theory, Algorithms Design,
   Machine Learning, Computer Systems, Computer Graphics
\end{itemize}

\section{Research \& Work}
\begin{tabu}{@{}l   X[r] }
  \textbf{Research Assistant} & Oct 2018 - Present\\
\emph{Advised by Prof. Robert Harper, Comp. Sci. Dept} & Pitt., PA
\end{tabu}
\vspace{-5pt}

\begin{itemize}
\itemsep-2pt
\item Developing dependent type theory for complexity analysis.
\end{itemize}

\begin{tabu}{@{}l X[r]  }
  \bfseries{Research Assistant} &  Feb 2017 - Oct 2018\\
\emph{Advised by Prof. Jan Hoffmann, Comp. Sci. Dept.} &Pitt., PA 
\end{tabu}
\vspace{-5pt}

\begin{itemize}
\itemsep-2pt
\item Designed a big-step garbage-collected cost semantics for Resource Aware ML (RaML)
\item Extended RaML type system to account for effects of garbage collection on heap usage
\item Implemented cost semantics in OCaml with support for OCaml syntax
\item Enhanced RaML with nested pattern matching (supports OCaml patterns such as data constructors, tuples, or patterns, aliases, etc)
\end{itemize}

\newpage
\begin{tabu}{@{}l  X[r]}
  \bfseries{Teaching Assistant} & Fall 2016\\
\emph{Comp. Sci. Department} & Pitt., PA
\end{tabu}
\vspace{-5pt}

\begin{itemize}
\itemsep-2pt
\item Formal Languages, Automata, and Computability (Fall 2016, Fall 2017)
\item Functional Programming (Summer 2017)
\end{itemize}


\begin{tabu}{@{}l X[r]}
  \textbf{Software Dev. Intern} & May - Aug 2016 \\
\emph{Viavi Solutions} & Colorado Springs, CO
\end{tabu}
\vspace{-5pt}

\begin{itemize}
\itemsep-2pt
\item Designed an accelerated data-plane packet receiver using Intel's Data Plane Dev. Kit (DPDK) 
\item Engineered a modular architecture using C++11 around the C API
\item Increased receiving throughput from 2-3Gbps to 10Gbps
\item Ensured Inter-operability with the Linux kernel networking stack
\end{itemize}

\begin{tabu}{@{}l X[r]}
  \textbf{Software Dev. Intern} & May - Aug 2016 \\
\emph{Testive} &Boston, MA
\end{tabu}
\vspace{-5pt}

\begin{itemize}
\itemsep-2pt
\item Collaborated with other interns to develop a cross platform mobile application
\item Coordinated development of core functionality
\item Employed the OpenCV (computer vision) API to parse image files into user input
\item Integrated backend logic into existing Django code base
\end{itemize}


\iffalse
\section{Projects}

\begin{tabu}{@{}>{\bfseries}c ? c  X[r]}
C0 Compiler & \emph{Haskell} & Aug - Dec 2016
\end{tabu}
\vspace{-5pt}

\begin{itemize}
\itemsep-2pt
\item Designed a complete compiler for a C-like language with safe-memory semantics
\item Built unsafe-memory mode and standard -O0, -O1, and -O2 optimization levels
\item Extended compiler to support LLVM textual IR as output format
\item Streamlined pipeline to target multiple backend architectures (ARM, x86-64)
\end{itemize}

\fi
% \begin{tabu}{@{}>{\bfseries}c ? c X[r]}
% Scalable Vector Graphics (SVG) Software Renderer & \emph{C++} & Oct 2016
% \end{tabu}
% \vspace{-5pt}
% 
% \begin{itemize}
% \itemsep-2pt
% \item Built support for basic shapes: points, lines, triangles
% \item Implemented anti-aliasing via super-sampling
% \item Devised mipmap levels and linear interpolation for texture mapping
% \end{itemize}

\section{Publications}

\bibliographystyle{unsrt}
\nocite{*}\bibliography{resume}

\section{Academic Talks}
\begin{tabu}{@{}l X[l]}
  \textbf{Automatic Space Bound Analysis for Programs with Garbage Collection} & Nov 2018\\
  \emph{Logic for Programming, Artificial Intelligence, and Reasoning 22} & Awassa Ethiopia
\end{tabu}

\begin{tabu}{@{}l X[l]}
  \textbf{Automatic Space Bound Analysis for Programs with Garbage Collection} & Sep 2018\\
\emph{PLunch @ CMU} & Pitt., PA
\end{tabu}

\end{document}
